A Random Choice SPH Scheme with Adaptive Viscosity

### 2021-01-13 CPMManuscript.tex
add author

\author{First Author         \and
        Second Author %etc.
}

@@

\institute{F. Author \at
              first address \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{fauthor@example.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Author \at
              second address
}

>>>>

\author{Zhixuan Cao \and Abani Patra \and  E. Bruce Pitman %etc.
}

@@

\institute{Zhixuan Cao \at
             MAE department, SUNY Buffalo, Buffalo, NY, USA
             \and
             Abani Patra \at
	  MAE department, SUNY Buffalo, Buffalo, NY, USA \\
	  \emph{Present address: Robinson Hall, Room 258, 200 College Avenue, Medford, MA, UAS } \\
	 \email{abani.patra@tufts.edu} 
	 \and
	  E. Bruce Pitman \at
            Department of Materials Design and Innovation, SUNY Buffalo, Buffalo, NY, USA
}
